---
title: "Case Study 6"
author: "Hannah Cope"
date: "10/4/2021"
output: 
  html_document:
    code_folding: 'hide'
---

#### Load Package
```{r}
library(tidyverse)
library(gridExtra)
```

### Diamond Length Plot
```{r}
ggplot(data = diamonds, aes(x)) +
  geom_histogram(fill = 'pink', color = 'black') +
  xlim(3,10) +
  theme_bw() +
  labs(x = "Length (mm)",
       y = "Number of \nLength Observations",
       title = "Diamond Lengths")
```

### Diamond Width Plot
```{r}
ggplot(data = diamonds, aes(y)) +
  geom_histogram(fill = 'lavender', color = 'black') +
  xlim(3,10) +
  theme_bw() +
  labs(x = "Width (mm)",
       y = "Number of \nWidth Observations",
       title = "Diamond Widths")
```

### Diamond Depth Plot
```{r}
ggplot(data = diamonds, aes(z)) +
  geom_histogram(fill = 'lightblue', color = 'black') +
  xlim(1,7) +
  theme_bw() +
  labs(x = "Depth (mm)",
       y = "Number of \nDepth Observations",
       title = "Diamond Depths")
```

### Diamond Prices Plot
```{r}
ggplot(data = diamonds, aes(price)) +
  geom_histogram(fill = 'yellow', color = 'black') +
  theme_bw() +
  labs(x = "Price ($)",
       y = "Number of \nPrice Observations",
       title = "Diamond Prices")
```
It was very surprising to that there are so many diamonds with prices less than $5000. I expected there to be a lot more diamonds with larger prices. 

### Different Effects on Prices
```{r}
carat <- ggplot(data = diamonds, aes(x = carat, y = price)) +
  geom_point() +
  theme_bw() +
  labs(x = "Carat",
       y = "Price",
       title = "The Effect of Price Based \non the Carat")

cut <- ggplot(data = diamonds, aes(x = cut, y = price)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Cut",
       y = "Price",
       title = "The Effect of Price Based \non the Cut")

color <- ggplot(data = diamonds, aes(x = color, y = price)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Color",
       y = "Price",
       title = "The Effect of Price Based \non the Color")

clarity <- ggplot(data = diamonds, aes(x = clarity, y = price)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Clarity",
       y = "Price",
       title = "The Effect of Price Based \non the Clarity")

grid.arrange(carat, color, cut, clarity, nrow = 2)
```
From these I am able to tell that the carat has the most effect on the price of the diamond. As the weight of the diamond increase, the price increases significantly.

### Carat vs. Cut Plot
```{r}
ggplot(data = diamonds, aes(x = carat, y = cut)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Carat",
       y = "Cut",
       title = "Diamond Cut vs. Carat")
```
There is only a slight correlation between cut and carat. The better the cut of the diamond, the carat tends to get smaller. This means that lower quality diamonds are going to be more expensive because the carat is the variable that affects the price the most. 

### Carat vs. Price Groups Plot
```{r}
diamond_prices <- diamonds %>%
  mutate(price_groups = 
           case_when(
             price >= 0 & price <= 2000 ~ "1-2000",
             price >= 2001 & price <= 4000 ~ "2001-4000",
             price >= 4001 & price <= 6000 ~ "4001-6000",
             price >= 6001 & price <= 8000 ~ "6001-8000",
             price >= 8001 & price <= 10000 ~ "8001-10000",
             price >= 10001 & price <= 12000 ~ "10001-12000",
             price >= 12001 & price <= 14000 ~ "12001-14000",
             price >= 14001 & price <= 16000 ~ "14001-16000",
             price >= 16001 & price <= 18000 ~ "16001-18000",
             price >= 18001 & price <= 20000 ~ "18001-20000"))
         
ggplot(data = diamond_prices, aes(carat, fct_reorder(price_groups, carat), fill = price_groups)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Carat",
       y = "Price",
       title = "Carats in Different Price Groups") +
  theme(legend.position = 'none')
```

### Large vs. Small Diamond Prices Plot
```{r}
large <- diamonds %>%
  filter(carat >= 4.01)

largeplot <- ggplot(data = large, aes(x = price)) +
  geom_histogram(fill = 'orange', color = 'black') +
  theme_bw() +
  labs(x = "Price",
       y = "Number of Large Diamons",
       title = "Prices of Large Carat Diamonds")

small <- diamonds %>%
  filter(carat <= 1.2)

smallplot <- ggplot(data = small, aes(x = price)) +
  geom_histogram(fill = 'lightgreen', color = 'black') +
  theme_bw() +
  labs(x = "Price",
       y = "Number of Small Diamonds",
       title = "Prices of Small Carat Diamonds")

grid.arrange(largeplot, smallplot, nrow = 1)
```
There are clearly a lot more small diamonds than there are large, but from this data I can tell that the smaller the diamond the lower the price. The prices of larger diamonds begins at the maximum price for a smaller diamond. This is what I expected. 

### Combined Plot of Carat, Cut, and Price
```{r}
ggplot(data = diamonds, aes(x = carat, y = price, fill = cut)) +
  geom_boxplot() +
  facet_wrap(~ cut, nrow = 1, scales = 'free') +
  theme_bw() +
  labs(x = "Carat",
       y = "Price",
       title = "Relationship Between Carat, Cut, and Price") +
  theme(legend.position = 'none')
```



