---
title: "Case Study 8"
author: "Hannah Cope"
date: "10/28/2021"
output: 
  html_document:
    code_folding: 'hide'
    keep_md: TRUE
---

#### Load Packages
```{r}
library(tidyverse)
library(stringi)
```

#### Load in Data
```{r}
bible <- read_csv(url("https://github.com/WJC-Data-Science/DTS350/raw/master/bible.csv"))
names <- read_csv(url("https://github.com/WJC-Data-Science/DTS350/raw/master/Names.csv"))
```

#### Filter out Old Testament Data and Make it a String
```{r}
OldTest <- bible %>%
  filter(volume_id == 1) %>%
  select(scripture_text) %>%
  str_c()
```

#### Filter out New Testament Data and Make it a String
```{r}
NewTest <- bible %>%
  filter(volume_id == 2) %>%
  select(scripture_text) %>%
  str_c()
```

### Find Savior Names in Old Testament
```{r}
OldTest %>%
  str_extract_all(names$name)
```

### Find Savior Names in New Testament
```{r}
NewTest %>%
  str_extract_all(names$name)
```

### Replace Savior Names with Placeholder in order to Split the String and Count the Words Inbetween
```{r}
notSaviorNames <- function(df, case) {
  for (names in names$name) {
    place_holder <- str_replace_all(df, names, "savior")
  }
  split <- str_split(place_holder, "savior")
  remove_split <- str_remove_all(split, "\n")
  if (case == "mean") {
    stri_stats_latex(unlist(remove_split))[[4]] / length(unlist(split))
  } else {
    stri_stats_latex(unlist(remove_split)) [[4]]
  }
}
```

### Count the Number of Words Inbetween the Savior Names of the Old Testament
```{r}
notSaviorNames(OldTest, "between")
```

### Count the Number of Words Inbetween the Savior Names of the New Testament
```{r}
notSaviorNames(NewTest, "between")
```

### Find the Mean of the Number of Words Inbetween the Savior Names of the Old Testament
```{r}
notSaviorNames(OldTest, "mean")
```

### Find the Mean of the Number of Words Inbetween the Savior Names of the New Testament
```{r}
notSaviorNames(NewTest, "mean")
```

I was able to find that there were a lot more words between the Savior Names in the Old Testament than the New Testament. Like in the Task, this could be because the Old Testament was very repetitive and had a lot of parts simplified and minimized in the New Testament. 

