---
title: "Task5Markdown"
author: "Hannah Cope"
date: "9/15/2021"
output: 
  html_document:
    theme: cosmo
    keep_md: True
    code_folding: 'hide'
---

### Load Packages
```{r}
library(tidyverse)
library(downloader)
library(readxl)
```

### Load in data
```{r}
SoloData <- tibble(read_csv("solo-artist-followers.csv"))
SoloData
BillboardData <- tibble(read_csv("billboard-hits.csv"))
BillboardData
tail(BillboardData)
```
##### All of the data types seem to have added in correctly.

### Remove signers who do not have at least 6 times they have had a top 100 hit.
```{r}
top100 <- BillboardData %>%
  group_by(name) %>%
  filter(n() >6 & band != "")
top100
tail(top100)
```

### Find the corresponding data in the data set for the top singers' bands.
```{r}
top_bands <- BillboardData %>% 
  group_by(band) %>%
  filter(name %in% top100$band)
top_bands
```
##### The band name showed up in the name column, so I am going to switch it into the band column.
```{r}
top_bands <- rename(top_bands, band = name, name = band)
top_bands
```
### Graph the data 
```{r}
ggplot(data = top100, aes(x = peak_date, y = peak_rank, color = name, group = name)) +
  geom_point() +
  geom_line() +
  geom_point(data = top_bands, color = "black") +
  geom_line(data = top_bands, color = "black", linetype = "dotted") +
  facet_wrap(~ band, scales = "free") +
  ylab("Peak Rank") +
  xlab("Peak Date") +
  scale_color_discrete("Name") +
  theme_bw()
```
From this plot I can tell that the top artist help give the band top 100 ranked songs. New Edition and Jonas Brothers show to have a lot of top songs reguardless of the singer though. 

## Data Sources

Data for overseas trade index for the June 2021 quarter
https://www.stats.govt.nz/large-datasets/csv-files-for-download/
```{r}
overseas <- tibble(read_csv("overseas-trade-indexes-June-2021-quarter-provisional-csv.csv"))
overseas
```

Research and development servery from 2016-2019
https://www.stats.govt.nz/large-datasets/csv-files-for-download/
```{r}
research <- tibble(read_csv("research-and-development-survey-2016-2019-csv.csv"))
research
```

Household living-costs price indexes in June 2021 quarter
https://www.stats.govt.nz/large-datasets/csv-files-for-download/
```{r}
household <- tibble(read_csv("Household-living-costs-price-indexes-June-2021-quarter-group-facts.csv"))
household
```

