---
title: "CaseStudy4"
author: "Hannah Cope"
date: "9/20/2021"
output: 
  html_document:
    theme: cosmo
    keep_md: True
    code_folding: 'hide'
---

### Load Packages
```{r}
library(nycflights13)
library(tidyverse)
library(ggrepel)
```

#### 2. Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airline?
```{r Select only Delta Airlines data}
lowest_late_arrival <- flights %>%
  filter(carrier == "DL")
lowest_late_arrival
```

```{r}
ggplot(data = lowest_late_arrival, mapping = aes(x = sched_arr_time, y = arr_delay, color = origin)) + 
  geom_point() +
  labs(x = "Scheduled Arrival Time",
       y = "Arrival Delay")
```
#### This plot shows that the JFK origin is most likely the best to minimize the chances of a late arrival time with Delta Airlines. This airport seems to have the most flights that arrived before the scheduled arrival time.

#### 3. Which destination airport is the worst airport for arrival time?
```{r Find the average delay time fro each airport}
delay <- flights %>%
  group_by(origin) %>%
  summarise(
    avg_delay = mean(arr_delay, na.rm = TRUE))
delay
```

```{r}
ggplot(data = flights, aes(x = origin, y = arr_delay)) +
  geom_point(aes(color = origin)) +
  geom_point(data = delay, aes(y = avg_delay, size = 1)) +
  annotate("text", x = c(1.2,2.2,3.2), y = 10, label = c("9.11", "5.55", "5.78")) +
  labs(x = "Destination Airport", 
       y = "Arrival Delay") +
  theme(legend.position = "none")
```
#### This plot shows that airport EWR has the worst arrival times. I was able to find the average arrival time for each airport and EWR ended up being the highest by almost double the amount of minutes as the other two airports.
